Rheology of Cubic Blue Phases

### 2012-11-07 trunk/papers/bprheo/bprheo.tex
Updated pictures and Tab.1
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1808 40876441-3496-0410-a613-a2fca35b2ae2

\begin{table*}[htpb]
\begin{tabular}{|c|| c || c |c |c||c| c| c||c| c| c|}
\hline
$\dot{\gamma}$ & $q_0$ & $\bar{v}_{x,min}$ & $\bar{v}_{x,max}$ & $\bar{v}_{x,std}$ & $\bar{v}_{y,min}$ & $\bar{v}_{y,max}$ & $\bar{v}_{y,std}$ & $\bar{v}_{z,min}$ & $\bar{v}_{z,max}$ & $\bar{v}_{z,std}$ \\
\hline
BPI \\
\hline
0.244 & 0.1388 &-15.79 &15.57 &1.04 &-0.89 &0.91 &0.95 &-1.59 &1.19 &1.27 \\
0.488 &0.1388 &-31.11 &31.25 &1.31 &-0.93 &0.98 &1.28 &-1.62 &1.10 &1.40 \\
0.976 &0.1388 &-62.24 &62.37 &2.51 &-1.31 &1.25 &2.68 &-1.24 &0.87 &2.65 \\
1.95 & 0.1388 &-124.65 &124.82 &3.62&  -2.49 &2.50 &4.51 &-1.89 & 1.62 &3.51 \\
3.91 &0.1388 &-248.69 &248.74 &3.90&  -3.31 &3.35 &4.21 &-2.56 & 2.88 &4.39 \\
7.81 &0.1388 &-497.22 &496.16 &4.46 &-6.49 &6.56 &7.99 &-5.31 & 7.46 &6.81 \\ 
15.63 &0.1388 &-992.46 &993.18 &10.36 &-3.08 &3.17 &10.49 &\bf{-2.87} & \bf{3.57} &10.54 \\
15.63 &-0.1388 &-992.46 &993.18 &10.36 &-3.08 &3.17 &10.49 &\bf{-3.57} & \bf{2.87} &10.54 \\
31.25 &0.1388 & -1988.36 &1986.71 &16.85 &-4.08 &4.46 &15.94 &-11.37 & 12.16 &19.38\\
62.50 &0.1388 & -4039.41 &3995.3  & 20.57 & -62.63 & 62.13 & 24.68 &-73.52 & 110.76 & 33.26 \\
\hline
BPII \\
\hline
0.244 &0.1963 &-7.75 &7.70 &0.13 &-0.17 &0.17 &0.13 &-0.24 &0.23 &0.19 \\
0.488 &0.1963 &-15.50 &15.40 &0.19 &-0.32 &0.30 &0.21 &-0.43 &0.42 &0.29 \\
0.976 &0.1963 &-31.01 &30.80 &0.33 &-0.60 &0.58 &0.41 &-0.85 &0.79 &0.47 \\
1.95 & 0.1963 &-62.04  &61.60 & 0.97 & -1.09 &1.07 & 0.76 & -1.64 & 1.55 & 0.81\\
3.91 & 0.1963 &-123.93 &123.18 & 1.76 &-1.66 &1.70 & 1.45 &-3.09& 2.73 &1.47\\
7.81 &0.1963  &-247.67 &246.45 & 3.20 &-2.62 &2.71 & 2.67 &-5.78 & 4.77 &2.74\\
15.63 &0.1963 &-494.85 &493.09 & 5.64 &-3.13 &3.31 &4.24 &\bf{-10.00} & \bf{7.66} &4.33\\
15.63 &-0.1963&-494.85 &493.09 & 5.64 & -3.13 &3.31 &4.24 &\bf{-7.66} & \bf{10.00} &4.33\\
31.25 &0.1963 &-988.73 &985.93 &8.96  &-1.79 &1.82 &5.86 &-14.39 & 11.04 &6.35\\
62.50 &0.1963 & -1969.41  & 1969.41 & 3.07 & -1.20 & 1.20 & 0.38 &-0.96 & 1.48 &0.38 \\
\hline
\end{tabular}
\caption{Time-averaged velocity components in shear flow for BPI ($\tau=-0.5, \kappa=1.0$) and BPII ($\tau=-0.5, \kappa=2.0$): Given are minimum and maximum values in $10^{-5}$ lattice units and the maximum standard deviation over the entire time sequence excluding any transient dynamics.}
\label{tab1}
\end{table*}

@@

\begin{figure}[htpb]
\includegraphics[width=0.4\textwidth]{disc-160k_run902.png}
\includegraphics[width=0.4\textwidth]{disc-164k_run902.png}
\includegraphics[width=0.4\textwidth]{disc-165k_run902.png}
\caption{Disclination network of BPII in shear flow: 
The pictures show a typical sequence of snapshots in the steady state 
at $\gd=1.56\e{-4}$ and time steps $t=1.60, 1.64,1.65\e{5}$. The velocity 
gradient is oriented along the vertical direction, whereas the 
horizontal direction is the flow direction. Lees-Edwards boundary 
conditions have been imposed in such a way that network moves to the 
right in the upper half and to the left in the lower half of the picture.}
\label{bp2-med}
\end{figure}

@@

\begin{figure*}[htpb]
\includegraphics[width=0.32\textwidth]{disc-xy-400k_run1115.png}
\includegraphics[width=0.32\textwidth]{disc-yz-400k_run1115.png}
\includegraphics[width=0.32\textwidth]{disc-xy-700k_run1115.png}\\
\includegraphics[width=0.32\textwidth]{disc-xy-750k_run1115.png}
\includegraphics[width=0.32\textwidth]{disc-xy-1700k_run1115.png}
\includegraphics[width=0.32\textwidth]{disc-xy-2200k_run1115.png}
\caption{Snapshots of BPI disclination network at $\dot{\gamma}=4.88\e{-6}$: 
Depicted is the transition from flow-induced, intertwined helices that 
undergo a recurring affine transformation (top left and centre, both at 
time step $t=4.0\e{5}$; top right at time step $t=7.0\e{5}$) with an intermediate 
conformation that is non-helical (bottom left at time step $t=7.5\e{5}$) 
to a distorted state (bottom centre at time step $t=1.7\e{6}$) and 
finally to an amorphous network (bottom right at $t=2.2\e{6}$). 
The picture at the top centre shows the network in gradient direction.
All other pictures have the view along the vorticity direction.}
\label{bp1-low}
\end{figure*}

@@

\begin{figure}[htpb]
%\includegraphics[width=0.4\textwidth]{dir+z-300k_run916.png}
\includegraphics[width=0.4\textwidth]{dir+z-301k_run916.png}
\includegraphics[width=0.4\textwidth]{dir+z-302k_run916.png}
\caption{Director field of BPI at high shear rate: The pictures show a slice 
of $L_x\times L_y = 64\times64$ lattice sites along the vorticity direction 
with the flow/gradient direction oriented along the horizontal/vertical axis. 
The colour code gives the magnitude of the in-plane component of the director field. 
The data is translationally invariant in vorticity direction.}
\label{bp1-high}
\end{figure}

@@

>>>>

\begin{table*}[htpb]
\begin{tabular}{|c||c|| c || c || c |c |c||c| c| c||c| c| c|}
\hline
& $\dot{\gamma}$ & ${\it Er}$ & $q_0$ & $\bar{v}_{x,min}$ & $\bar{v}_{x,max}$ & $\bar{v}_{x,std}$ & $\bar{v}_{y,min}$ & $\bar{v}_{y,max}$ & $\bar{v}_{y,std}$ & $\bar{v}_{z,min}$ & $\bar{v}_{z,max}$ & $\bar{v}_{z,std}$ \\
\hline
BPI \\
\hline
AN & 0.244 & 0.08& 0.1388 &-15.79 &15.57 &1.04 &-0.89 &0.91 &0.95 &-1.59 &1.19 &1.27 \\
AN & 0.488 & 0.17 & 0.1388 &-31.11 &31.25 &1.31 &-0.93 &0.98 &1.28 &-1.62 &1.10 &1.40 \\
AN & 0.976 & 0.33 & 0.1388 &-62.24 &62.37 &2.51 &-1.31 &1.25 &2.68 &-1.24 &0.87 &2.65 \\
AN & 1.95 & 0.67 & 0.1388 &-124.65 &124.82 &3.62&  -2.49 &2.50 &4.51 &-1.89 & 1.62 &3.51 \\
\hline
3D-PRC & 3.91 & 1.33 & 0.1388 &-248.69 &248.74 &3.90&  -3.31 &3.35 &4.21 &-2.56 & 2.88 &4.39 \\
3D-PRC & 7.81 & 2.67 & 0.1388 &-497.22 &496.16 &4.46 &-6.49 &6.56 &7.99 &-5.31 & 7.46 &6.81 \\ 
3D-PRC & 15.63 & 5.33 & 0.1388 &-992.46 &993.18 &10.36 &-3.08 &3.17 &10.49 &\bf{-2.87} & \bf{3.57} &10.54 \\
3D-PRC & 15.63 & 5.33 & -0.1388 &-992.46 &993.18 &10.36 &-3.08 &3.17 &10.49 &\bf{-3.57} & \bf{2.87} &10.54 \\
3D-PRC & 31.25 &10.67 & 0.1388 & -1988.36 &1986.71 &16.85 &-4.08 &4.46 &15.94 &-11.37 & 12.16 &19.38\\
3D-PRC & 46.87 & 15.99 & 0.1388 & -3025.46 & 3003.05 &21.43 & -56.96 & 56.44  & 18.75 & -12.65 & 82.97  & 27.96\\
\hline
2D-DTR & 62.50 & 21.33& 0.1388 & -4039.41 &3995.3  & 20.57 & -62.63 & 62.13 & 24.68 &-73.52 & 110.76 & 33.26 \\
2D-DTR &78.125 &26.66 & 0.1388 & -4968.11 &4973.75 &20.89 &-60.61 &58.75 &23.66 &-84.93 &116.61 &34.75 \\
\hline
1D-CH & 93.75 &32.00 & 0.1388 & -5955.12 &5948.84 & 0.71 & -0.002 & 0.002 & -  & -16.45 & 16.03 &0.62 \\
1D-CH & 125.0 & 42.66& 0.1388 & -7934.97 & 7935.41 & 0.36 & -0.005 & 0.005 & - &-22.73 & 21.12 & 0.07\\
\hline
FAN & 187.5 & 63.99& 0.1388 &-11906.4  &119064 &0.36 &- &- &- &-0.68 & 0.38 & 0.05\\
\hline

BPII \\
\hline
3D-PRC & 0.244 &0.04 & 0.1963 &-7.75 &7.70 &0.13 &-0.17 &0.17 &0.13 &-0.24 &0.23 &0.19 \\
3D-PRC & 0.488 &0.08 & 0.1963 &-15.50 &15.40 &0.19 &-0.32 &0.30 &0.21 &-0.43 &0.42 &0.29 \\
3D-PRC & 0.976 &0.17 & 0.1963 &-31.01 &30.80 &0.33 &-0.60 &0.58 &0.41 &-0.85 &0.79 &0.47 \\
3D-PRC & 1.95 &0.33  & 0.1963 &-62.04  &61.60 & 0.97 & -1.09 &1.07 & 0.76 & -1.64 & 1.55 & 0.81\\
3D-PRC &3.91 & 0.67& 0.1963 &-123.93 &123.18 & 1.76 &-1.66 &1.70 & 1.45 &-3.09& 2.73 &1.47\\
3D-PRC &7.81 &1.33 & 0.1963  &-247.67 &246.45 & 3.20 &-2.62 &2.71 & 2.67 &-5.78 & 4.77 &2.74\\
3D-PRC &15.63 & 2.67& 0.1963 &-494.85 &493.09 & 5.64 &-3.13 &3.31 &4.24 &\bf{-10.00} & \bf{7.66} &4.33\\
3D-PRC & 15.63 & 2.67& -0.1963&-494.85 &493.09 & 5.64 & -3.13 &3.31 &4.24 &\bf{-7.66} & \bf{10.00} &4.33\\
3D-PRC & 31.25 &5.34 & 0.1963 &-988.73 &985.93 &8.96  &-1.79 &1.82 &5.86 &-14.39 & 11.04 &6.35\\
\hline
1D-THW & 46.87 &8.00 & 0.1388 & -1476.75 & 1476.84 &1.69 &-0.35  &0.35  & 0.17 &-0.23 &0.23  & 0.22\\
1D-THW & 62.50 & 10.67& 0.1963 & -1969.41  & 1969.41 & 3.07 & -1.20 & 1.20 & 0.38 &-0.96 & 1.48 &0.38 \\
\hline
1D-CH & 78.125 & 13.33 &  0.1388 &-2458.60 & 2458.61  &0.37 &- &- &- &-18.54 &16.94 &0.32 \\
1D-CH & 93.75 &16.00 & 0.1388 &-2950.2  &2950.2 &0.50 &- &- &- &-22.69 & 19.72 & 0.04\\
\hline
FAN & 125.0 &21.33 & 0.1388 &-3937.31  & 3937.32 &0.28 &-  &-  &-  &-1.79 &1.15  &0.14 \\
\hline
\end{tabular}
\caption{Minima, maxima and standard deviation of time-averaged velocity components 
for BPI ($\tau=-0.5, \kappa=1.0$) and BPII ($\tau=-0.5, \kappa=2.0$) in steady 
shear flow: All values are given in $10^{-5}$ lattice units. The transient dynamics 
has not been included in the averaging procedure. The regimes comprise periodically 
recurring conformation (3D-PRC), two-dimensional double twist rolls (2D-DTR), 
one-dimensional helix (1D-CH), one-dimensional travelling helical wave (1D-THW) 
and a flow-aligned nematic state (FAN).}
\label{tab1}
\end{table*}

@@

\begin{figure}[htpb]
\includegraphics[width=0.41\textwidth]{disc-160k_run902.png}
\includegraphics[width=0.41\textwidth]{disc-164k_run902.png}
\includegraphics[width=0.41\textwidth]{disc-165k_run902.png}
\caption{Disclination network of BPII in shear flow: 
The pictures show a typical sequence of snapshots in the steady state 
at $\gd=1.56\e{-4}$ and time steps $t=1.60, 1.64,1.65\e{5}$. The velocity 
gradient is oriented along the vertical direction, whereas the 
horizontal direction is the flow direction. Lees-Edwards boundary 
conditions have been imposed in such a way that network moves to the 
right in the upper half and to the left in the lower half of the picture.}
\label{bp2-med}
\end{figure}

@@

\begin{figure*}[htpb]
\includegraphics[width=0.245\textwidth]{disc-xy-10k_run1115.png}
\includegraphics[width=0.245\textwidth]{disc-xy-180k_run1115.png}
\includegraphics[width=0.245\textwidth]{disc-xy-200k_run1115.png}
\includegraphics[width=0.245\textwidth]{disc-xy-210k_run1115.png}\\
\includegraphics[width=0.245\textwidth]{disc-xy-400k_run1115.png}
\includegraphics[width=0.245\textwidth]{disc-xy-700k_run1115.png}
\includegraphics[width=0.245\textwidth]{disc-xy-750k_run1115.png}
\includegraphics[width=0.245\textwidth]{disc-xy-2200k_run1115.png}
\caption{Snapshots of BPI disclination network at $\dot{\gamma}=4.88\e{-6}$: 
Depicted is the transition from flow-induced, intertwined helices that 
undergo a recurring affine transformation (top left and centre, both at 
time step $t=4.0\e{5}$; top right at time step $t=7.0\e{5}$) with an intermediate 
conformation that is non-helical (bottom left at time step $t=7.5\e{5}$) 
to a distorted state (bottom centre at time step $t=1.7\e{6}$) and 
finally to an amorphous network (bottom right at $t=2.2\e{6}$). 
The picture at the top centre shows the network in gradient direction.
All other pictures have the view along the vorticity direction.}
\label{bp1-low}
\end{figure*}

@@

\begin{figure}[htpb]
\includegraphics[width=0.45\textwidth]{dir3d-z-302k_run916.png}
\caption{Director field of BPI at high shear rate: The pictures show a slice 
of $L_x\times L_y \times L_Z= 32\times32\times 32$ lattice sites along the vorticity direction 
with the flow/gradient direction oriented along the horizontal/vertical axis. 
The colour code gives the magnitude of the in-plane component of the director field. 
The data is translationally invariant in vorticity direction.}
\label{bp1-high}
\end{figure}

@@

\subsection{Transition to cholesteric helix and flow-aligned nematic state}

\begin{figure}[htpb]
\includegraphics[width=0.45\textwidth]{dir3d+y-200k_run1179.png}
\caption{}
\label{cholflow}
\end{figure}
